---
title: "cda_final"
date: "2023/6/2"
output: html_document
---

```{r setup, include=FALSE,warning=F}
knitr::opts_chunk$set(echo = TRUE)
options(digits=5)
library(car)
library(MASS)
library(brglm2)
library(tidyverse)
library(dplyr)
library(corrplot)
library(pROC)
```

```{r}
data <- read.csv("train_cleaned.csv", header = T)
```


#### Correlation 
```{r,fig.height=6.5, fig.width=6.5, fig.align="center"}
data <- data[,-1]
colnames(data) <- c("x1","x2","x3","x4","x5","x6","x7","x8","x9",
                    "x10","x11","x12","x13","x14","x15","x16","x17","x18",
                    "x19","x20","x21","x22","y")
data_fac <- data
cor <- data.frame (round(cor(data[,1:23],method = "spearman"),2))
corrplot(cor(data[,1:23]), method = 'color', addCoef.col = 'black', type = 'upper', tl.srt = 45, number.cex = .5, number.font = 1,tl.col = "black")
```

\newpage 

### Quasi-seperation 處理資料  

因為有出現x=0, y=0 時的樣本數為0 ，因此需要處理它，避免造成之後模型產生quasi-complete separation，處理方式為合併至下一個level. 

#### X10
```{r}
xtabs(~x10+ y, data=data_fac)
for (i in c(1:length(data_fac$x10))){
  data_fac$x10[i] <- ifelse(data_fac$x10[i]==0, 1, next)
}
xtabs(~x10+ y, data=data_fac)
```
 
#### X14
```{r}
#xtabs(~x14+ y, data=data_fac)
for (i in c(1:length(data_fac$x14))){
   data_fac$x14[i] <- ifelse(data_fac$x14[i]==0, 1, next)
}
xtabs(~x14+ y, data=data_fac)
```

#### X15
```{r}
#xtabs(~x15+ y, data=data_fac)
for (i in c(1:length(data_fac$x15))){
   data_fac$x15[i] <- ifelse(data_fac$x15[i]==0, 1, next)
}
xtabs(~x15+ y, data=data_fac)
```
#### X19
```{r}
#xtabs(~x19+ y, data=data_fac)
for (i in c(1:length(data_fac$x19))){
   data_fac$x19[i] <- ifelse(data_fac$x19[i]==0, 1, next)
}
xtabs(~x19+ y, data=data_fac)
```

\newpage 
#### X20
```{r}
#xtabs(~x20+ y, data=data_fac)
for (i in c(1:length(data_fac$x20))){
   data_fac$x20[i] <- ifelse(data_fac$x20[i]==0, 1, next)
}
xtabs(~x20+ y, data=data_fac)
```

## Model_1    
以讓effect 顯著為目的，用LRT檢定模型表現  

### Full Model
```{r}
data_fac[1:23] = lapply(data_fac[1:23], factor)
full_model <- glm(y~ .,family=binomial,data=data_fac)
summary(full_model)
formula(full_model)
```

### Only significance effect
```{r}
fit <- glm(y~ . -x1-x6-x21,family=binomial,data=data_fac)
summary(fit)
```

### Transformation:
#### X9  
將levels=12的合併為0:
```{r}
data_tran <- data_fac
data_tran$x9 <- fct_recode(data_fac$x9, "0"="1","0"="2")
fit_tranx9 <- glm(y~ . -x1-x6-x21,family=binomial,data=data_tran)
summary(fit_tranx9)
```

#### LRT for x9
```{r}
anova(fit_tranx9, fit, test="LRT")
```

Conclusion: Better performance. 

#### X10  
將levels=23的合併為1 :
```{r}
data_tran$x10 <- fct_recode(data_fac$x10, "1"="2","1"="3")
fit_tranx10 <- glm(y~ . -x6-x1-x21,family=binomial,data=data_tran)
summary(fit_tranx10)
```

#### LRT for x10
```{r}
anova(fit_tranx10, fit_tranx9, test="LRT")
```

Conclusion: No need for transformation 

#### X13  
將levels=5的合併至1 :
```{r}
data_tran$x10 <- data_fac$x10
data_tran$x13 <- fct_recode(data_fac$x13, "1"="5")
fit_tranx13 <- glm(y~ . -x6-x1-x21,family=binomial,data=data_tran)
summary(fit_tranx13)
```

#### LRT for x13
```{r}
anova(fit_tranx13, fit_tranx9, test="LRT")
```

Conclusion: Better performance. 

#### X15   
將levels=2的合併至1:
```{r}
data_tran$x15 <- fct_recode(data_fac$x15, "1"="2")
fit_tranx15 <- glm(y~ . -x6-x1-x21,family=binomial,data=data_tran)
summary(fit_tranx15)
```

#### LRT for x15
```{r}
anova(fit_tranx15, fit_tranx13, test="LRT")
```

Conclusion: Better performance after transformation. 

#### X16 
將levels=5的合併至4:
```{r}
data_tran$x16 <- fct_recode(data_fac$x16, "3"="1", "3"="2")
fit_tranx16 <- glm(y~ . -x6-x1-x21,family=binomial,data=data_tran)
summary(fit_tranx16)
```

#### LRT for x16
```{r}
anova(fit_tranx16, fit_tranx15, test="LRT")
data_tran$x16 <- data_fac$x16
```

Conclusion: No need for transformation.  

#### X20   
將levels=2的合併至1:
```{r}
data_tran$x20 <- fct_recode(data_fac$x20, "1"="2")
fit_tranx20 <- glm(y~ . -x6-x1-x21,family=binomial,data=data_tran)
summary(fit_tranx20)
```

#### LRT for x20
```{r}
anova(fit_tranx20, fit_tranx15, test="LRT")
anova(fit_tranx20, fit, test="LRT")
anova(fit_tranx20, full_model, test="LRT")
```

Conclusion: Better performance. 

### Conclusion for Model1  
- x9 (Ease of Online booking):(0)(1)(2)(3)(4)(5) $\to$ (012)(3)(4)(5)
- X13 (Seat comfort):(1)(2)(3)(4)(5) $\to$ (15)(2)(3)(4) 
- X15 (On-board service):(1)(2)(3)(4)(5) $\to$ (12)(3)(4)(5)
- X20 (Cleanliness):(1)(2)(3)(4)(5) $\to$ (12)(3)(4)(5)
```{r}
formula(fit_tranx20)
summary(fit_tranx20)
```

#### Fit the test data
#### Transform the data
```{r}
data_test <- read.csv("test_cleaned(1).csv", header = T)
data_test <- data_test[,-1]
colnames(data_test) <- c("x1","x2","x3","x4","x5","x6","x7","x8","x9",
                    "x10","x11","x12","x13","x14","x15","x16","x17","x18",
                    "x19","x20","x21","x22","y")
```


```{r}
#xtabs(~x14+ y, data=data_test)
for (i in c(1:length(data_test$x14))){
  data_test$x14[i] <- ifelse(data_test$x14[i]==0, 1, next)
}

#xtabs(~x15+ y, data=data_test)
for (i in c(1:length(data_test$x15))){
  data_test$x15[i] <- ifelse(data_test$x15[i]==0, 1, next)
}

#xtabs(~x19+ y, data=data_test)
for (i in c(1:length(data_test$x19))){
  data_test$x19[i] <- ifelse(data_test$x19[i]==0, 1, next)
}
```


```{r}
data_test[1:23] = lapply(data_test[1:23], factor)
data_test_fac <- data_test
data_test_fac$x9 <- fct_recode(data_test$x9, "0"="1","0"="2")
data_test_fac$x13 <- fct_recode(data_test$x13, "1"="5")
data_test_fac$x15 <- fct_recode(data_test$x15, "1"="2")
data_test_fac$x20 <- fct_recode(data_test$x20, "1"="2")
```

#### Prediction 
```{r}
probabilities <- fit_tranx20 %>% predict(data_test_fac, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, 1, 0) #看要設多少
mean(predicted.classes == data_test_fac$y) #accuracy
confusion_matrix <- matrix(xtabs(~ data_test_fac$y + predicted.classes),nrow=2)
confusion_matrix
```

```{r}
rocplot <- roc(y ~ probabilities, data=data_test_fac)
plot.roc(rocplot, legacy.axes=TRUE) # 不確定要不要放圖
auc(rocplot)
```


### Model-2
#### Stepwise logistic regression  

使用AIC 當作指標  
```{r}
# step_model <- step(full_model, direction = "backward", trace=1)
# summary(step_model)
# formula(step_model)
step_model <- glm(y ~ x1+x2+x3+x4+x5+x6+x7+x8+x9+x10+x11+x12+x13+x14+x15+x16
                  +x17+x18+x19+x20+x22, family = binomial, data = data_fac)
```

#### Prediction 
```{r}
probabilities <- step_model %>% predict(data_test, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, 1, 0) #看要設多少
mean(predicted.classes == data_test$y) #accuracy
confusion_matrix <- matrix(xtabs(~ data_test$y + predicted.classes),nrow=2)
confusion_matrix
```

```{r}
rocplot <- roc(y ~ probabilities, data=data_test)
plot.roc(rocplot, legacy.axes=TRUE) # 不確定要不要放圖
auc(rocplot)
```

### Model-3
#### consider the collinearity  

使用AIC 當作指標  
#### GVIF
```{r}
library(glmtoolbox)
gvif(full_model)
```
#### Remove x14
```{r}
fit3_tran14 <- glm(y~ . -x14,family=binomial,data=data_fac)
summary(fit3_tran14) 
gvif(fit3_tran14)
```
#### Remove x9
```{r}
fit3_tran9 <- glm(y~ . -x9,family=binomial,data=data_fac)
summary(fit3_tran9) 
gvif(fit3_tran9)
```
#### Remove x9,x14
```{r}
fit3_tran914 <- glm(y~ . -x9-x14,family=binomial,data=data_fac)
summary(fit3_tran914)
gvif(fit3_tran914)
```
#### Choose model
By AIC of three models,fit3_tran9 is better since its the smallest AIC.

#### Fit the test data
```{r}
data_test3 <- read.csv("test_cleaned(1).csv", header = T)
data_test3 <- data_test3[,-1]
colnames(data_test3) <-c("x1","x2","x3","x4","x5","x6","x7","x8","x9","x10","x11","x12","x13","x14","x15","x16","x17","x18","x19","x20","x21","x22","y")
```


```{r}
#xtabs(~x14+ y, data=data_test)
for (i in c(1:length(data_test3$x14))){
  data_test3$x14[i] <- ifelse(data_test3$x14[i]==0, 1, next)
}

#xtabs(~x15+ y, data=data_test)
for (i in c(1:length(data_test3$x15))){
  data_test3$x15[i] <- ifelse(data_test3$x15[i]==0, 1, next)
}

#xtabs(~x19+ y, data=data_test)
for (i in c(1:length(data_test3$x19))){
  data_test3$x19[i] <- ifelse(data_test3$x19[i]==0, 1, next)
}
```


#### Prediction
```{r}
probabilities3 <- fit3_tran9%>% predict(data_test, type = "response")
predicted.classes3 <- ifelse(probabilities3 > 0.5, 1, 0) #看要設多少
mean(predicted.classes3 == data_test$y) #accuracy
confusion_matrix3 <- matrix(xtabs(~ data_test$y + predicted.classes3),nrow=2)
confusion_matrix3
```

```{r}
rocplot <- roc(y ~ probabilities3, data=data_test)
plot.roc(rocplot, legacy.axes=TRUE) # 不確定要不要放圖
auc(rocplot)
```



